The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-04-24 paper/ms.tex
updated section 2 including captions

For each photon in the simulation we have its initial position inside
the sphere, direction of propagation $\hat{k}_{in}$ and reduced
frequency $x_{in}$. The photon's propagation stops once they cross the
surface of the sphere. At this point we store the position, the outgoing direction
of propagation $\hat{k}_{out}$ and the reduced frequency $x_{out}$. We
define the angle $\theta$ by $\cos\theta = \hat{k}_{\rm obs}\cdot
\hat{k}$, that is the angle of the line of sight with
respect to the direction of the angular velocity. Following the notation
implemented in \cite{Zheng2013}. %we make the study of the anisotropic emission in
%terms of this angle.

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{f8.eps}
\end{center}
\caption{Geometry
    \label{fig:CentralSpec}}  
\end{figure}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{spectraCentral.eps}
\end{center}
\caption{
2D histogram showing the number of photons that escape with frecuency
$x$ forming an angle $\theta$ (parameterized as $\cos\theta$) with the
rotationa axis. The rotational velocity ($0,100,200,300$\kms)
increases from left to right and the optical depth ($10^5$, $10^6$,
$10^7$) from top to bottom. 
\label{fig:CentralSpec} }   
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.8\textwidth]{spectraHOM.eps}
\end{center}
\caption{Homogeneous
    \label{fig:HOMSpec}}  
\end{figure*}

@@

Additionally, we have used two independently developed Monte Carlo
codes \citep{CLARA,DijkstraKramer} to perform the calculations of the
non-dusty models. The results we report are robust in the sense
that they are obtained by both codes.

@@

The central results of this paper is summarized in Figures
\ref{fig:CentralSpec} and \ref{fig:HOMSpec}. These figures shows
that rotation fix a preferred axis for both photons distributions, 
this implies that our systems doesn't have spherical symmetry and
we have to take into account the viewing angle $\theta$ for all
of our posterior analysis.

>>>>

For each photon in the simulation we have its initial position inside
the sphere, direction of propagation $\hat{k}_{\rm in}$ and reduced
frequency $x_{\rm in}$. The photon's propagation stops once they cross the
surface of the sphere. At this point we store the position, the outgoing direction
of propagation $\hat{k}_{\rm out}$ and the reduced frequency $x_{\rm
  out}$. We now define the angle $\theta$ by $\cos\theta = \hat{k}_{\rm out}\cdot
\hat{k}\equiv \mu$, it is the angle of the outgoing photons with 
respect to the direction of the angular velocity. We use the variable $\mu$ to
study the anisotropy induced by rotation. Figure \ref{fig:geometry}
shows the geometry of the problem and the important variables.

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{f8.eps}
\end{center}
\caption{Geometry of the gas distribution. The angular velocity vector
  is parallel to the unit vector $\hat{k}$. In order to describe the
  departures from spherical symmetry we use the polar angle $\theta$
  formed by the direction of the outgoing photons with respecto to the
  $z$-axis. We define define the variable $\mu\equiv\cos\theta$ to
  report to present our results.
    \label{fig:geometry}}  
\end{figure}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{spectraCentral.eps}
\end{center}
\caption{
2D histogram showing the number of photons that escape with frecuency
$x$ forming an angle $\theta$ (parameterized as $\cos\theta$) with the
rotationa axis. The rotational velocity ($0,100,200,300$\kms)
increases from left to right and the optical depth ($10^5$, $10^6$,
$10^7$) from top to bottom. The \ly photons are initialized at the
center of the sphere.
\label{fig:CentralSpec} }   
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{spectraHOM.eps}
\end{center}
\caption{Same as Figure \ref{fig:CentralSpec} for \ly photons
  initialized homogeneously throughout the sphere.
    \label{fig:HomSpec}}  
\end{figure*}

@@

Additionally, we have used two independently developed Monte Carlo
codes \citep{CLARA,DijkstraKramer} to perform the calculations. The
results we report are robust in the sense that they are obtained by
both codes.

@@

The central results of this paper are summarized in Figures
\ref{fig:CentralSpec} and \ref{fig:HomSpec}. They show 2D histograms
of escape frequency $x$ and escape angle parameterized by
$\cos\theta$.

that rotation fix a preferred axis for both photons distributions, 
this implies that our systems doesn't have spherical symmetry and
we have to take into account the viewing angle $\theta$ for all
of our posterior analysis.
